Supplementary Material for ``LUCID: Learning-Enabled Uncertainty-Aware Certification of Stochastic Dynamical Systems''

### 2025-08-11 docs/paper/figures/steps.tex
feat: update paper
feat: submitted

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[node distance=0.6cm and 0.9cm,
            input-block/.style={rectangle, draw, fill=white, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
            output-block/.style={rectangle, draw, fill=green!20, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
            block/.style={rectangle, draw, fill=accent!20, text width=3.7cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
            arrow/.style={thick,->,>=Stealth},
            tool/.style={rectangle, draw, fill=green!20, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
            inv/.style={}, 
            arrow/.style={thick,->,>=latex}
        ]

@@

        % Lucid blocks
        \node[block, right=of samples] (estimator) {Fit the estimator 
        $\E[f(X_+)\!\mid\! X=x,A=a]$
        % $\hat{f}\colon \X\times\A \to \X$
        };
        \node[block, below=of estimator] (feature) {Construct the feature map $\phi_M\colon \X \to \mathbb{R}^{2M+1}$};
        \node[block, below=of feature] (lattice) {Construct lattices on $\X, \X_0, \X_u$};
        \node[block, below=of lattice] (apply-lattice) {Apply the feature map to the lattice points};
        \node[block, below=of apply-lattice] (optimizer) {Solve the LP};
        \node[draw, dashed, inner sep=0.3cm, rounded corners,
        fit=(estimator)(feature)(lattice)(apply-lattice)(optimizer), label=above:{\textbf{\lucid}}] {};

        \node[input-block, left=of lattice] (specification) {Specify $\X, \X_0, \X_u$};

@@

    \end{tikzpicture}
    \caption{Sequence of steps \lucid goes through to generate a barrier certificate.}
    \label{fig:steps}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[node distance=0.4cm and 0.9cm,
            input-block/.style={rectangle, draw, fill=white, text width=2.9cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
            output-block/.style={rectangle, draw, fill=green!20, text width=2.9cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
            block/.style={rectangle, draw, fill=accent!20, text width=3.7cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
            arrow/.style={thick,->,>=Stealth},
            tool/.style={rectangle, draw, fill=green!20, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
            inv/.style={}, 
            arrow/.style={thick,->,>=latex}
        ]

@@

        % Lucid blocks
        \node[block, right=of samples] (estimator) {Fit the estimator 
        $\E[f(X_+)\!\mid\! X=x,A=a]$
        % $\hat{f}\colon \X\times\A \to \X$
        };
        \node[block, below=of estimator] (feature) {Construct the feature map $\phi_M\colon \X \to \mathbb{R}^{2M+1}$};
        \node[block, below=of feature] (lattice) {Construct lattices on $\X, \X_0, \X_U$};
        \node[block, below=of lattice] (apply-lattice) {Apply the feature map to the lattice points};
        \node[block, below=of apply-lattice] (optimizer) {Solve the LP};
        \node[draw, dashed, inner sep=0.3cm, rounded corners,
        fit=(estimator)(feature)(lattice)(apply-lattice)(optimizer), label=above:{\textbf{\lucid}}] {};

        \node[input-block, left=of lattice] (specification) {Specify $\X, \X_0, \X_U$};

@@

    \end{tikzpicture}
    \caption{Sequence of steps \lucid goes through to generate a barrier certificate.}
    \vspace{-0.5cm}
    \label{fig:steps}
\end{figure}
